Associations between Chlorophyll \emph{a} and various Microcystin-LR Health Advisory Concentrations

### 2015-09-16 manuscript/manuscript.tex
up through draft of results done

\title{Associations between Chlorophyll \emph{a} and various Microcystin-LR
Health Advisory Concentrations}
\author{
Jeffrey W. Hollister
Betty J. Kreakie
Dorothy Q. Kellog
}
\date{}

\begin{document}
%%Edited by @jhollist 09/15/2014
%%Adds title from YAML
\begin{singlespace}
\begin{center}
\huge Associations between Chlorophyll \emph{a} and various Microcystin-LR
Health Advisory Concentrations
\end{center}
%%Adds Author, correspond email asterisk, and affilnum from YAML
\begin{center}
\large
Jeffrey W. Hollister \textsuperscript{*} \textsuperscript{1} 
Betty J. Kreakie \textsuperscript{1} 
Dorothy Q. Kellog \textsuperscript{2} 
\end{center}
%%Adds affiliations from YAML
\begin{justify}
\footnotesize \emph{ 
\\*
\textsuperscript{1}US Environmental Protection Agency, Office of Research and Development,
National Health and Environmental Effects Research Laboratory, Atlantic
Ecology Division, 27 Tarzwell Drive Narragansett, RI, 02882, USA\\*
\\*
\textsuperscript{2}University of Rhode Island, Department of Natural Resources Science,
Kingston, RI, 02882, USA\\*
}
%%Adds corresponding author email(s) from YAML
\newcounter{num}
\setcounter{num}{1}
\\[0.1cm]
\footnotesize \emph{ 
\ifnum\value{num}=1%
\textsuperscript{*} corresponding author:
\fi
\href{mailto:hollister.jeff@epa.gov}{\nolinkurl{hollister.jeff@epa.gov}}
\stepcounter{num}
}
\end{justify}
%%Adds date from YAML
\normalsize

@@

Cyanobacteria harmful algal blooms (cHABs) are associated with a wide
range of adverse health effects that stem mostly from the presence of
cyanotoxins. To help protect against these impacts, several health
advisory levels have been set for some toxins. In particular, one of the
more common toxins, microcystin, has several advisory levels set for
drinking water and recreational use and managing water bodies to meet
those levels could have far reaching benefits. However, compared to
other water quality measures, measurements of microcystin are not common
and current field measurement techniques have limited precision and
accuracy. Addressing these issues will take time and resources. Thus,
there is utility in finding indicators of microcystin that are already
widely available, can be estimated quickly and \emph{in situ}, and used
as a first defense against high levels of microcystin. In particular,
chlorophyll \emph{a} is very commonly measured, can be estimated
\emph{in situ}, and has been shown to be positively associated with
microcystin. In this paper we use this association to provide estimates
of chlorophyll \emph{a} that if exceeded would be indicative of a higher
probability of exceeding select health advisory concentrations for
microcystin-LR. Using the 2007 National Lakes Assessment and a
conditional probability approach that has been used in other water
quality settings, we identify chlorophyll \emph{a} concentrations that
are more likely than not to be associated with an exceedance of a
microcystin health advisory level. We look at the recent US EPA
standards for drinking water as well as the World Health Organization
levels for drinking water and recreational use. For microcystin
concentrations of 0.3, 1, 1.6, and 2 we find chlorophyll \emph{a}
concentrations of 20.8, 78.29, 109.66, and 109.66, respectively. When
managing for these various microcystin levels exceeding these reported
chlorophyll \emph{a} concentrations should be a trigger for further
testing and possible management action.

@@

We used the 2007 National Lakes Assessment (NLA) water quality and
microcystin-LR concentration data {[}REF{]}. The NLA is a probability
based design that, when using the provided sample weights, can be used
to provide unbiased estimates of lake condition for all lakes in the
original sample frame (e.g.~lakes greater than 4ha in the conterminous
US). These data represent a snapshot of water quality from the summer of
2007 and data on chlorophyll \emph{a} and microcystin-LR concentrations
are available for lakes. All results are reported using weighted
estimates.

@@

We used a conditional probability analysis (CPA) approach to explore
associations between chlorophyll \emph{a} concentrations and World
Health Organization (WHO) and U.S. Environmental Protection Agency (U.S.
EPA) microcystin-LR health advisory levels {[}REFS{]}. Many levels have
been suggested {[}Table \ref{tab:microcystin_levels}{]}, but lakes with
higher microcystin-LR concentrations in the NLA were rare. Only 1.16 \%
of lakes sampled had a concentration greater than 10. Thus, for this
analysis we focus on the microcystin concentrations that are better
represented in the NLA data. These were 0.3, 1, 1.6, and 2 \(\mu\)g/L.

A detailed discussion of CPA is beyond the scope of this paper, but see
Paul et al. {[}-REF{]} and Hollister et al. {[}-REF{]} for details. For
this analysis, we used CPA to examine how the conditional probability of
exceeding one of the health advisory changes as chlorophyll \emph{a}
increases in a lake. The 95\% confidence intervals were calculated from
1000 bootstrapped samples. To identify chlorophyll \emph{a}
concentrations of concern we used a 50\% conditional probability of
exceeding each health advisory level and extracted the minimum
chlorophyll \emph{a} concentration that was associated with the upper
confidence level being 50\% or greater. Details of the specific
implementation we used are available at
\url{https://github.com/USEPA/microcystinchla}.

@@

(Table \ref{tab:mc_chla_table})

(Figure \ref{fig:chla_micro_scatter})

(Figure \ref{fig:chla_micro_cdf})

(Figure \ref{fig:multi_cp_plot})

@@

\begin{figure}[htbp]
\centering
\includegraphics{manuscript_files/figure-latex/chla_micro_scatter-1.pdf}
\caption{Scatterplot showing association betweeen chlorophyll
\it{a} and microcystin-LR. \label{fig:chla_micro_scatter}}
\end{figure}

\begin{verbatim}
## No id variables; using all as measure variables
\end{verbatim}

\begin{figure}[htbp]
\centering
\includegraphics{manuscript_files/figure-latex/chla_micro_cdf-1.pdf}
\caption{Conditional probability plots showing association between the
probability of exceeding various microcystin-LR (MLR) health advisory
Levels. \label{fig:chla_micro_cdf}}
\end{figure}

@@

\begin{longtable}[c]{@{}lll@{}}
\toprule
\begin{minipage}[b]{0.11\columnwidth}\raggedright\strut
Source
\strut\end{minipage} &
\begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
Type
\strut\end{minipage} &
\begin{minipage}[b]{0.20\columnwidth}\raggedright\strut
Concentration
\strut\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
WHO
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Drinking
\strut\end{minipage} &
\begin{minipage}[t]{0.20\columnwidth}\raggedright\strut
1 \(\mu\)g/L
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
U.S. EPA
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Drinking
\strut\end{minipage} &
\begin{minipage}[t]{0.20\columnwidth}\raggedright\strut
0.3 \(\mu\)g/L
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
U.S. EPA
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Drinking
\strut\end{minipage} &
\begin{minipage}[t]{0.20\columnwidth}\raggedright\strut
1.6 \(\mu\)g/L
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
WHO
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Recreational
\strut\end{minipage} &
\begin{minipage}[t]{0.20\columnwidth}\raggedright\strut
2-4 \(\mu\)g/L
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
WHO
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Recreational
\strut\end{minipage} &
\begin{minipage}[t]{0.20\columnwidth}\raggedright\strut
10-20 \(\mu\)g/L
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
WHO
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Recreational
\strut\end{minipage} &
\begin{minipage}[t]{0.20\columnwidth}\raggedright\strut
20-2000 \(\mu\)g/L
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
WHO
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Recreational
\strut\end{minipage} &
\begin{minipage}[t]{0.20\columnwidth}\raggedright\strut
\textgreater{}2000 \(\mu\)g/L
\strut\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[c]{@{}llll@{}}
\toprule
\begin{minipage}[b]{0.11\columnwidth}\raggedright\strut
Source
\strut\end{minipage} &
\begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
Type
\strut\end{minipage} &
\begin{minipage}[b]{0.17\columnwidth}\raggedright\strut
Microcystin
\strut\end{minipage} &
\begin{minipage}[b]{0.17\columnwidth}\raggedright\strut
Chlorophyll
\strut\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
U.S. EPA
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Drinking
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
0.3
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
20.8
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
WHO
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Drinking
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
1
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
78.29
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
U.S. EPA
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Drinking
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
1.6
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
109.7
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
WHO
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Recreational
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
2
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
109.7
\strut\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

>>>>

\title{Associations between Chlorophyll \emph{a} and various Microcystin-LR
Health Advisory Concentrations}
\author{
Jeffrey W. Hollister
Betty J. Kreakie
}
\date{}

\begin{document}
%%Edited by @jhollist 09/15/2014
%%Adds title from YAML
\begin{singlespace}
\begin{center}
\huge Associations between Chlorophyll \emph{a} and various Microcystin-LR
Health Advisory Concentrations
\end{center}
%%Adds Author, correspond email asterisk, and affilnum from YAML
\begin{center}
\large
Jeffrey W. Hollister \textsuperscript{*} \textsuperscript{1} 
Betty J. Kreakie \textsuperscript{1} 
\end{center}
%%Adds affiliations from YAML
\begin{justify}
\footnotesize \emph{ 
\\*
\textsuperscript{1}US Environmental Protection Agency, Office of Research and Development,
National Health and Environmental Effects Research Laboratory, Atlantic
Ecology Division, 27 Tarzwell Drive Narragansett, RI, 02882, USA\\*
}
%%Adds corresponding author email(s) from YAML
\newcounter{num}
\setcounter{num}{1}
\\[0.1cm]
\footnotesize \emph{ 
\ifnum\value{num}=1%
\textsuperscript{*} corresponding author:
\fi
\href{mailto:hollister.jeff@epa.gov}{\nolinkurl{hollister.jeff@epa.gov}}
\stepcounter{num}
}
\end{justify}
%%Adds date from YAML
\normalsize

@@

Cyanobacteria harmful algal blooms (cHABs) are associated with a wide
range of adverse health effects that stem mostly from the presence of
cyanotoxins. To help protect against these impacts, several health
advisory levels have been set for some toxins. In particular, one of the
more common toxins, microcystin, has several advisory levels set for
drinking water and recreational use and managing water bodies to meet
those levels could have far reaching benefits. However, compared to
other water quality measures, measurements of microcystin are not common
and current field measurement techniques have limited precision and
accuracy. Addressing these issues will take time and resources. Thus,
there is utility in finding indicators of microcystin that are already
widely available, can be estimated quickly and \emph{in situ}, and used
as a first defense against high levels of microcystin. In particular,
chlorophyll \emph{a} is very commonly measured, can be estimated
\emph{in situ}, and has been shown to be positively associated with
microcystin. In this paper we use this association to provide estimates
of chlorophyll \emph{a} that if exceeded would be indicative of a higher
probability of exceeding select health advisory concentrations for
microcystin-LR. Using the 2007 National Lakes Assessment and a
conditional probability approach that has been used in other water
quality settings, we identify chlorophyll \emph{a} concentrations that
are more likely than not to be associated with an exceedance of a
microcystin health advisory level. We look at the recent US EPA
standards for drinking water as well as the World Health Organization
levels for drinking water and recreational use. For microcystin
concentrations of 0.3, 1, 1.6, and 2 we find chlorophyll \emph{a}
concentrations of 23.68, 63.94, 89.71, and 102.6, respectively. When
managing for these various microcystin levels exceeding these reported
chlorophyll \emph{a} concentrations should be a trigger for further
testing and possible management action.

@@

We used the 2007 National Lakes Assessment (NLA) water quality and
microcystin-LR concentration data {[}REF{]}. These data represent a
snapshot of water quality from the summer of 2007 and data on
chlorophyll \emph{a} and microcystin-LR concentrations are available for
lakes.

@@

We used a conditional probability analysis (CPA) approach to explore
associations between chlorophyll \emph{a} concentrations and World
Health Organization (WHO) and U.S. Environmental Protection Agency (U.S.
EPA) microcystin-LR health advisory levels (Paul and Munns 2011). Many
levels have been suggested (Table \ref{tab:microcystin_levels}), but
lakes with higher microcystin-LR concentrations in the NLA were rare.
Only 1.16 \% of lakes sampled had a concentration greater than 10. Thus,
for this analysis we focus on the microcystin concentrations that are
better represented in the NLA data. These were 0.3, 1, 1.6, and 2
\(\mu\)g/L.

A detailed discussion of CPA is beyond the scope of this paper, but see
Paul et al. {[}-REF{]} and Hollister et al. {[}-REF{]} for details. For
this analysis, we used CPA to examine how the conditional probability of
exceeding one of the health advisory changes as chlorophyll \emph{a}
increases in a lake. The 95\% confidence intervals were calculated from
1000 bootstrapped samples. To identify chlorophyll \emph{a}
concentrations of concern we used a 50\% conditional probability of
exceeding each health advisory level and extracted the minimum
chlorophyll \emph{a} concentration that was associated with the upper
confidence level being 50\% or greater. As both microcystin-LR and
chlorophyll \emph{a} values were both highely skewed right, a log base
10 transformation was used. Additional details of the specific
implementation are available at
\url{https://github.com/USEPA/microcystinchla}.

@@

In the 2007 NLA, microcystin-LR concentrations ranged from 0.05 to 225.
Microcystin-LR concentrations of 0.05 \(\mu\)g/L represent the detection
limits. Any value greater than that indicates the presence of
microcystin-LR. Of those lakes with microcystin, the median
concentration was 0.51 and the mean was 0.51. Lastly, of all lakes
sampled, 21\% of lakes exceeded the U.S. EPA childrens drinking water
standard, 8.8\% of lakes exceeded the U.S. EPA adult drinking water
standard,11.7\% of lakes exceeded the WHO drinking water standard,and
7.3\% of lakes exceeded the WHO recreational standard. For chlorophyll
\emph{a}, the range was 0.07 to 936. All lakes had reported chlorophyll
\emph{a} concentrations that exceeded detection limits. The median
concentration was 7.79 and the mean was 29.6301946.

The association between Log 10 microcystin-LR and Log 10 chlorophyll
\emph{a} show a wedge pattern (Figure \ref{fig:chla_micro_scatter}).
This indicates that higher concentrations of microcystin-LR almost
always co-occur with higher concentrations of chlorophyll \emph{a} yet
the inverse is not true. Higher chlorophyll \emph{a} is not necessarily
predictive of higher microcystin-LR concentrations; however, chlorophyll
\emph{a} may be predictive of the probability of exceeding a certian
concentration. This is the case as the probability of exceeding each of
the four tested health adviroy levels shos this patern of probability of
exceeding the advisory level increases as a function of chlorophyll
\emph{a} concentration (Figure \ref{fig:multi_cp_plot}).

We use this association to identify chlorophyll \emph{a} concentrations
that are associated with greater than even odds of exceeding a given
health advisory level (Table \ref{tab:mc_chla_table}). These represent
27.7831559\%,
\texttt{100*(length(nla\_dat\$CHLA{[}nla\_dat\$CHLA\textgreater{}=mc\_chla{[}2{]}{]})/length(nla\_dat\$CHLA))}\%,
\texttt{100*(length(nla\_dat\$CHLA{[}nla\_dat\$CHLA\textgreater{}=mc\_chla{[}3{]}{]})/length(nla\_dat\$CHLA))}\%,
and
\texttt{100*(length(nla\_dat\$CHLA{[}nla\_dat\$CHLA\textgreater{}=mc\_chla{[}4{]}{]})/length(nla\_dat\$CHLA))}\%
of sample lakes for the U.S EPA childrens drinking water, the WHO
drinking water, the U.S. EPA Adult drinking water, and the WHO
recreationsl standards, respecitvely.

@@

\begin{figure}[htbp]
\centering
\includegraphics{manuscript_files/figure-latex/chla_micro_scatter-1.pdf}
\caption{Scatterplot showing association betweeen chlorophyll \textit{a}
and microcystin-LR. \label{fig:chla_micro_scatter}}
\end{figure}

@@

\begin{longtable}[c]{@{}lll@{}}
\caption{Various suggested microcystin-LR health advisory
concentrations. \label{tab:microcystin_levels}}\tabularnewline
\toprule
\begin{minipage}[b]{0.11\columnwidth}\raggedright\strut
Source
\strut\end{minipage} &
\begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
Type
\strut\end{minipage} &
\begin{minipage}[b]{0.20\columnwidth}\raggedright\strut
Concentration
\strut\end{minipage}\tabularnewline
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{0.11\columnwidth}\raggedright\strut
Source
\strut\end{minipage} &
\begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
Type
\strut\end{minipage} &
\begin{minipage}[b]{0.20\columnwidth}\raggedright\strut
Concentration
\strut\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
WHO
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Drinking
\strut\end{minipage} &
\begin{minipage}[t]{0.20\columnwidth}\raggedright\strut
1 \(\mu\)g/L
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
U.S. EPA
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Drinking
\strut\end{minipage} &
\begin{minipage}[t]{0.20\columnwidth}\raggedright\strut
0.3 \(\mu\)g/L
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
U.S. EPA
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Drinking
\strut\end{minipage} &
\begin{minipage}[t]{0.20\columnwidth}\raggedright\strut
1.6 \(\mu\)g/L
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
WHO
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Recreational
\strut\end{minipage} &
\begin{minipage}[t]{0.20\columnwidth}\raggedright\strut
2-4 \(\mu\)g/L
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
WHO
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Recreational
\strut\end{minipage} &
\begin{minipage}[t]{0.20\columnwidth}\raggedright\strut
10-20 \(\mu\)g/L
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
WHO
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Recreational
\strut\end{minipage} &
\begin{minipage}[t]{0.20\columnwidth}\raggedright\strut
20-2000 \(\mu\)g/L
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
WHO
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Recreational
\strut\end{minipage} &
\begin{minipage}[t]{0.20\columnwidth}\raggedright\strut
\textgreater{}2000 \(\mu\)g/L
\strut\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[c]{@{}llll@{}}
\caption{Chlorophyll extit\{a\} concentrations that are associated with
a 50\% probability of exceeding a microcystin-LR health advisory
concentration. \label{tab:mc_chla_table}}\tabularnewline
\toprule
\begin{minipage}[b]{0.11\columnwidth}\raggedright\strut
Source
\strut\end{minipage} &
\begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
Type
\strut\end{minipage} &
\begin{minipage}[b]{0.17\columnwidth}\raggedright\strut
Microcystin
\strut\end{minipage} &
\begin{minipage}[b]{0.17\columnwidth}\raggedright\strut
Chlorophyll
\strut\end{minipage}\tabularnewline
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{0.11\columnwidth}\raggedright\strut
Source
\strut\end{minipage} &
\begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
Type
\strut\end{minipage} &
\begin{minipage}[b]{0.17\columnwidth}\raggedright\strut
Microcystin
\strut\end{minipage} &
\begin{minipage}[b]{0.17\columnwidth}\raggedright\strut
Chlorophyll
\strut\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
U.S. EPA
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Drinking
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
0.3
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
23.68
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
WHO
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Drinking
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
1
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
63.94
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
U.S. EPA
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Drinking
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
1.6
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
89.71
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
WHO
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Recreational
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
2
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
102.6
\strut\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

Paul, J. F., and W. R. Munns. 2011. Probability surveys, conditional
probability, and ecological risk assessment. Environmental Toxicology
and Chemistry 30:1488--1495.
